\LARGE \bf Energy-Aware Dynamic Mission Planning Algorithm for UAVs

### 2020-10-12 icra-2021.tex
fixes from the last meeting (attempt 1)

@@

The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path. Our goal is a mission extension by optimizing both QoS and TEEs as the UAV flies and its batteries drain. The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) nodes. It optimizes TEEs--an abstraction of the path to follow--and guides the UAV using a vector field that converges smoothly to the path. Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis. Data using a commercial fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.

The algorithm relies on the assumptions of the mission--a time-varying motion plan and a set of tasks the UAV is supposed to perform along the TEEs and QoS parameters constraints--being \emph{periodic} and \emph{uncertain}. The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather. We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state estimator to cope with the uncertainty assumption. The algorithm selects the controls (the QoS and TEEs parameters) using a robust output feedback model predictive control (MPC).

The remainder of the paper is organized as follows. The dynamic mission planning problem is set in Section~\ref{sec:prob}. A suitable model for the energy and position of the UAV in Section~\ref{sec:model}. The algorithm that uses the model and solves the problem is proposed in Section~\ref{sec:algo}. Section~\ref{sec:experimental} presents a fixed-wing UAV flying in an agricultural scenario showcasing the performance. The paper finishes with some conclusions in Section~\ref{sec:conclusion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem Statement}
\label{sec:prob}

We consider the problem of dynamic mission planning for a precision agriculture fixed-wing UAV. Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with mobile robots being increasingly used for e.g., harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}. The mission consist of a UAV flying in ellipses shifted in time, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a survey mission optimized for the craft's dynamics. Such a scenario is frequently put into practice, with complex monitoring strategies being often implemented utilizing UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.

The algorithm inputs the mission
\begin{equation}\label{eq:mission}
  \mathcal{M}:=\left\{\varphi_k,\,(\underline{c}_k,\overline{c}_k),\bigcup_{n=0,\dots,\rho-1}(\underline{\text{QoS}}_{k,n},\overline{\text{QoS}}_{k,n}):\,\forall k\in\mathbb{T}\right\},
\end{equation}
where $\mathbb{T}:=\,[0,t_f)\subseteq\mathbb{R}_{\geq 0}$ is the mission time, $t_f\in\mathbb{R}_{\geq 0}$ the final instant, $\varphi_k\in\mathbb{R}$ is a generic continuous twice differentiable TEE along its upper and lower bounds $(\underline{c}_k,\overline{c}_k)\in\mathbb{R}^2$ (the motion plan--an ordered pair), and a set of upper and lower bounds for the $\sigma$ tasks $(\underline{\text{QoS}}_{k,i},\overline{\text{QoS}}_{k,i})\in\mathbb{Z}_{\geq 0}^2$ (a set of also ordered pairs).

@@

It outputs the correction to the position and the instantaneous energy consumption, while it adapts the control $\mathbf{u}_k$ in function of the TEE and QoS parameters.

%%%%%%%%%%%%%%%
\section{Model}
\label{sec:model}

>>>>

%% hyperref
% and an override to make hyperref work with ieeeconf.cls
\makeatletter
\let\NAT@parse\undefined
\makeatother
\usepackage{hyperref}

@@

The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path. Our goal is a mission extension by optimizing both QoS and TEEs as the UAV flies and its batteries drain. The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) nodes. It optimizes TEEs--an abstraction of the path to follow--and guides the UAV using a vector field that converges smoothly to the path. 
%Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis. Data using a commercial fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.
It relies on the assumptions of the mission being \emph{periodic} and \emph{uncertain}. The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather. We propose the Fourier analysis to address the periodicity assumption--being the mission periodic, we expect the energy to evolve also periodically--and a state estimator to cope with the uncertainty assumption. The algorithm selects the controls (QoS and TEEs parameters) using robust output feedback model predictive control (MPC).

To show case the algorithm we consider the problem of dynamic mission planning for a precision agriculture fixed-wing UAV. Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with mobile robots being increasingly used for e.g., harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}. The mission consist of a UAV flying in ellipses shifted in time, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a survey mission optimized for the craft's dynamics. The algorithm plans the mission controlling the processing rate and the length of the semi-major and -minor axis. Such a scenario is frequently put into practice, with complex monitoring strategies being often implemented utilizing UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}. Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.

The remainder of the paper is organized as follows. The dynamic mission planning overview is set in Section~\ref{sec:prob}, along a suitable model for the energy and position of the UAV. The algorithm that uses the model and solves the problem is proposed in Section~\ref{sec:algo}. Section~\ref{sec:experimental} presents a fixed-wing UAV flying in an agricultural scenario showcasing the performance. The paper finishes with some conclusions in Section~\ref{sec:conclusion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Mission Planning Overview}
\label{sec:prob}

The mission is a time-varying motion plan and a set of tasks the UAV is supposed to perform along the TEEs and QoS parameters constraints
\begin{equation}\label{eq:mission}
  \mathcal{M}:=\left\{\varphi_k,\,(\underline{c}_k,\overline{c}_k),\bigcup_{n=0,\dots,\rho-1}(\underline{\text{QoS}}_{k,n},\overline{\text{QoS}}_{k,n}):\,\forall k\in\mathbb{T}\right\},
\end{equation}
where $\mathbb{T}:=\,[0,t_f)\subseteq\mathbb{R}_{\geq 0}$ is the mission time, $t_f\in\mathbb{R}_{\geq 0}$ the final instant, $\varphi_k\in\mathbb{R}$ is a generic continuous twice differentiable TEE along its upper and lower bounds $(\underline{c}_k,\overline{c}_k)\in\mathbb{R}^2$ (the motion plan--an ordered pair), and a set of upper and lower bounds for the $\sigma$ tasks $(\underline{\text{QoS}}_{k,i},\overline{\text{QoS}}_{k,i})\in\mathbb{Z}_{\geq 0}^2$ (a set of also ordered pairs).

@@

The algorithm inputs the mission and outputs the correction to the position and the instantaneous energy consumption, while it adapts the control $\mathbf{u}_k$ in function of the TEE and QoS parameters.

%%%%%%%%%%%%%%%
\subsection{Model}
\label{sec:model}
